---
output: github_document
---

# Mapping between Schema.Org and EML via JQ 



## Key References:

- [Google documentation for Dataset type](https://developers.google.com/search/docs/data-types/dataset)
- [Schema.Org Dataset spec](http://schema.org/Dataset)
- [Google Structured Data testing tool](https://search.google.com/structured-data/testing-tool)
- [Ecological Metadata Language (EML) Spec](https://knb.ecoinformatics.org/#external//emlparser/docs/eml-2.1.1/./eml.html)
- [JQ Query Language](https://stedolan.github.io/jq/tutorial/)

## Additional references

- [DataONE global repository](https://search.dataone.org/#data)
- [JSON-LD Playground](https://json-ld.org/playground/)
- [JSON-LD Spec](https://json-ld.org/spec/latest/json-ld/)
- [`emld` R package](https://github.com/cboettig/emld)


## Example files: 


- [hf205.json](../examples/hf205.json) Is a pretty extensive example of data structured in the EML-JSON format.
- [earthcube.json](../examples/earthcube.json) Is a pretty extensive example of data structured in the Schema.Org JSON format.

These example files should give you a good idea of how things are laid out in each case.

```{r}
library(jqr)
```


Load in the current working drafts of the JQ maps.  
You'll want to modify the `.jq` files so that they can map 
much more of the data.  



## EML to Schema.Org:

Let's map a more complete EML document into schema.org:

 | del( .[] |select(.givenName == null and .organizationName == null)) | unique
 
 [if .creator|type == "array" then .creator[] else .creator end
```{r}
getwd()
eml_to_schema <- readr::read_file("jq/eml_to_schema.jq")
eml <- readr::read_file("../examples/hf205.json")
jq(eml, eml_to_schema)

```


```{r}
eml_to_schema <- readr::read_file("jq/eml_to_schema.jq")
eml_citation50 <- readr::read_file("../examples/eml/eml-sample.json")
jq(eml_citation50, eml_to_schema)
```



## Schema.Org to EML

Convert a dataset marked up in <http://schema.org/Dataset> terms into EML


```{r}
schema_to_eml <-  readr::read_file("jq/schema_to_eml.jq")
schema <- readr::read_file("../examples/schema-org-dataset.json")
getwd()
eml <- jq(schema, schema_to_eml)
eml
```

```{r}/
schema_to_eml <-  readr::read_file("jq/schema_to_eml.jq")
schema <- readr::read_file("../examples/earthcube.json")
getwd()
eml_earthcube <- jq(schema, schema_to_eml)
eml_earthcube
```


